---
title: "p8105_HW5_yk2959"
author: "Kiran Kui"
date: "2022-11-12"
output: github_document
---

```{r load libraries}
library(tidyverse)
library(readxl)
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
```

# Problem 2

```{r}
homicide_df = read_csv("./data/homicide-data.csv") %>%
  janitor::clean_names() 

skimr::skim(homicide_df)
```

I have imported the homicide dataset from the github repository and tidied the names of the variables in the dataset. 

## Brief introduction of the raw homicide dataset 

The raw dataset contains `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns, with each row representing a single record of homicide in 50 large U.S. cities. 

Variables include, date of homicide, victim first and last name, victims' race, age, sex and the city/state that the homicide was located, as well as the lattitude and longitude of the homicide location, given in `r colnames(homicide_df)`. 

```{r}

homicide_df_clean_1 = homicide_df %>% 
  unite(city_state, c(city, state), sep = ", ", remove = FALSE) %>% 
  group_by(city_state) %>% 
  summarise(
    total_homicide = sum(!is.na(uid)))

homicide_df_clean_2 = homicide_df %>% 
  mutate(
  unsolved = ifelse(
  disposition %in% c('Closed without arrest', 'Open/No arrest'), 1, 0)) %>% 
  unite(city_state, c(city, state), sep = ", ", remove = FALSE) %>% 
  group_by(city_state, unsolved) %>% 
  filter(unsolved == 1) %>% 
  summarise(total_unsolved = sum(!is.na(unsolved))) %>% 
  select(-unsolved)

homicide_df_clean = merge(homicide_df_clean_1, homicide_df_clean_2, by='city_state', all.x=TRUE) %>% 
  drop_na(total_unsolved)

```
I have created a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides. 

```{r}
prop.test(
  homicide_df_clean %>%  filter(city_state == "Baltimore, MD") %>% pull(total_unsolved),
  homicide_df_clean %>%  filter(city_state == "Baltimore, MD") %>% pull(total_homicide)) %>% 
  broom::tidy()
  
```

I used the prop.test function to estimate the proportion of homicides that are unsolved, then saved the output of prop.test as an R object, and apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe. 

The estimated proportion of unsolved homicides is 0.646 and the confidence interval is (0.628, 0.663). 

```{r}
homicide_df_clean_tidy = 
  homicide_df_clean %>% 
  mutate(
    prop_test = map2(.x = total_unsolved, .y = total_homicide, ~ prop.test(x = .x, n = .y)),
    tidy_prop_test = map(.x = prop_test, ~ broom::tidy(.x))) %>%
  select(-prop_test) %>% 
  unnest(tidy_prop_test) %>% 
  select(city_state, estimate, conf.low,conf.high)

homicide_plot = homicide_df_clean_tidy %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + 
  labs(
    title = "Showing the estimates of unsolved homicides and CIs",
    x = "city/state", 
    y = "estimates of proportion of unsolved homicide "
  )

  
homicide_plot

```
 

