---
title: "p8105_HW5_yk2959"
author: "Kiran Kui"
date: "2022-11-12"
output: github_document
---

```{r load libraries}
library(tidyverse)
library(readxl)
library(dplyr)
library(purrr)
library(ggplot2)
```


# Problem 1

## Problem 1

I imported the data in individual spreadsheets contained in `./data/zip_data/` by creating a dataframe that includes the list of all files in that directory and the complete path to each file.  Then, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
data = 
  tibble(
    files = list.files(
      path = "./data/data/", all.files = TRUE,
      full.names = FALSE, recursive = TRUE,
      ignore.case = FALSE, include.dirs = TRUE, no.. = FALSE),
    path = str_c("data/data/", files)
    ) %>%
  mutate(results = map(path, read_csv)) %>% 
  unnest()
```

I tidied the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
data_tidy = 
  data %>%
  separate(files, into = c("status", "ID"), sep = "_") %>%
  mutate(
    ID = str_replace(ID, ".csv", "") 
  ) %>%
  select(-path) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>%
  mutate(week = as.numeric(week))
```

I created a plot showing individual data, faceted by group. 

```{r}
data_tidy %>% 
  ggplot(aes(x = week, y = outcome, color = status)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~status)
```

This plot suggests high within-subject correlation meaning that subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way.

# Problem 2

```{r}
homicide_df = read_csv("./data/homicide-data.csv") %>%
  janitor::clean_names() 

skimr::skim(homicide_df)
```

I have imported the homicide dataset from the github repository and tidied the names of the variables in the dataset. 

## Brief introduction of the raw homicide dataset 

The raw dataset contains `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns, with each row representing a single record of homicide in 50 large U.S. cities. 

Variables include, date of homicide, victim first and last name, victims' race, age, sex and the city/state that the homicide was located, as well as the lattitude and longitude of the homicide location, given in `r colnames(homicide_df)`. 

```{r}

homicide_df_clean_1 = homicide_df %>% 
  unite(city_state, c(city, state), sep = ", ", remove = FALSE) %>% 
  group_by(city_state) %>% 
  summarise(
    total_homicide = sum(!is.na(uid)))

homicide_df_clean_2 = homicide_df %>% 
  mutate(
  unsolved = ifelse(
  disposition %in% c('Closed without arrest', 'Open/No arrest'), 1, 0)) %>% 
  unite(city_state, c(city, state), sep = ", ", remove = FALSE) %>% 
  group_by(city_state, unsolved) %>% 
  filter(unsolved == 1) %>% 
  summarise(total_unsolved = sum(!is.na(unsolved))) %>% 
  select(-unsolved)

homicide_df_clean = merge(homicide_df_clean_1, homicide_df_clean_2, by='city_state', all.x=TRUE) %>% 
  drop_na(total_unsolved)

```
I have created a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides. 

```{r}
prop.test(
  homicide_df_clean %>%  filter(city_state == "Baltimore, MD") %>% pull(total_unsolved),
  homicide_df_clean %>%  filter(city_state == "Baltimore, MD") %>% pull(total_homicide)) %>% 
  broom::tidy()
  
```

I used the prop.test function to estimate the proportion of homicides that are unsolved, then saved the output of prop.test as an R object, and apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe. 

The estimated proportion of unsolved homicides is 0.646 and the confidence interval is (0.628, 0.663). 

```{r}
homicide_df_clean_tidy = 
  homicide_df_clean %>% 
  mutate(
    prop_test = map2(.x = total_unsolved, .y = total_homicide, ~ prop.test(x = .x, n = .y)),
    tidy_prop_test = map(.x = prop_test, ~ broom::tidy(.x))) %>%
  select(-prop_test) %>% 
  unnest(tidy_prop_test) %>% 
  select(city_state, estimate, conf.low,conf.high)

homicide_plot = homicide_df_clean_tidy %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
# remember to label! 

homicide_plot

```

# Problem 3

```{r}

my_function = function(samp_size = 30, mu = 0, sigma = 5){
  
  q3_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)) 
  
    t_test = 
     t.test(q3_data, conf.level = .95) %>% 
      broom::tidy()
}

simulation_df =
  tibble(
    mu = c(1, 2, 3, 4, 5, 6)
  ) %>% 
  mutate(
    result = map(.x = mu, ~rerun(5000, my_function(mu = .x))),
    result_df = map(result, bind_rows)
  ) %>% 
  unnest(cols = c("result_df")) %>% 
  select(-result)

```


I made a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. There is a positive association between effect size and power. 

```{r}

simulation_plot_1 = simulation_df %>% 
  mutate(
  rejected = ifelse(p.value < 0.05, 1, 0)) %>% 
  filter(rejected == 1) %>% 
  group_by(mu, rejected) %>% 
  summarise(prop_rejected = sum(!is.na(rejected))/5000) %>% 
  ggplot(aes(x = mu, y = prop_rejected)) +
  geom_point() + 
  labs(
    title = "Association Between Power(effect size) and True Mean",
    x = "True Mean", 
    y = "Power"
  )

simulation_plot_1

```

I made a plot showing the average estimate of mu hat on the y axis and the true value of mu on the x axis.

```{r}

simulation_plot_2 = simulation_df %>% 
  group_by(mu) %>% 
  summarise(mu_avg_estimate = sum(estimate)/5000) %>% 
  ggplot(aes(x = mu, y = mu_avg_estimate)) +
  geom_point() + 
  labs(
    title = "Association Between average estimate of mu hat and True Mean",
    x = "True Mean", 
    y = "Average estimate of mu hat"
  )

simulation_plot_2
```

I made a second plot for the average estimate of mu hat only in samples for which the null was rejected on the y axis and the true value of mu on the x axis. 


```{r}
simulation_plot_3 = simulation_df %>% 
  mutate(
  rejected = ifelse(p.value < 0.05, 1, 0)) %>% 
  filter(rejected == 1) %>% 
  group_by(mu, rejected) %>% 
  summarise(mu_avg_estimate = mean(estimate)) %>% 
  ggplot(aes(x = mu, y = mu_avg_estimate)) +
  geom_point() + 
  labs(
    title = "Association Between average estimate of mu only in samples for which the null was rejected and True Mean",
    x = "True Mean", 
    y = "Average estimate of mu hat"
  )

simulation_plot_3

```

The sample average of mu across tests for which the null is rejected approximately equal to the true value of mu. This is because the sample average of means derived from taking random samples from the population approximates the true mean. As our sample n=5000 is quite large, the sample average of means is a good approximate of the true mean. 




